---
title: "MiningSandbox-ISSTA"
author: "Rodrigo Bonifácio et al."
date: '2023-01-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=5, fig.height=5, fig.path='./figures/', dev=c('png', 'pdf'))

library(sqldf)
library(xtable)
```


### Loading the complete dataset

```{r fullDataSet}
full_ds <- read.csv("sample_final_ds.csv", head=T, sep=',')

colnames(full_ds)
nrow(full_ds)

full_ds <- sqldf("select * from full_ds where benign = 'True'")

nrow(full_ds)


# "sha256"      "family"      "malware"     "apidetected" "similarity"
```

### Computing basic statistics for similarity (complete dataset)

```{r similarityCDS}
summary(full_ds$similarity)
```

### Number of malwares (complete dataset)
```{r countMalwareCDS}
sqldf("select malware, count(*) from full_ds group by malware")
```

### Number of repackaged apps the MAS approach labels as malware (complete dataset)

```{r countLabeledAsMalwareCDS}
sqldf("select apidetected, count(*) from full_ds group by apidetected")
```


### Accuracy assesment (complete dataset)

```{r accuracyCDS}

tp <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'True'" )

fp <- sqldf("select * from full_ds where malware = 'False' and apidetected = 'True'" )

fn <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'False'" )

precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore
```

### Family Assessment (Complete Dataset)

```{r familyAssesmentCDS}
sqldf("select family, count(*) 
       from full_ds 
       where malware = 'True' 
       group by family order by 2 desc")


sqldf("select malware, apidetected, count(*) 
       from full_ds 
       where family = 'gappusin'
       group by malware, apidetected")

sqldf("select count(distinct family) from full_ds")


sqldf("select count(*) from full_ds where family = 'None'")

families <- sqldf("select family, count(*) as Total 
                   from full_ds where family != 'None'
                   group by family 
                  order by 2 desc")

sqldf("select family, total*100.0/662.0
       from families 
       group by family
       order by 2 desc")
```

```{r smallDataSet}
small_ds <- read.csv("samples_DL_final_ds.csv", head=T, sep=',')

colnames(full_ds)
nrow(full_ds)

# "sha256"      "family"      "malware"     "apidetected" "similarity"

summary(small_ds$similarity)

rp <- sqldf("select count(*) from small_ds where malware = 'True'")

tp <- sqldf("select * from small_ds where malware = 'True' and apidetected = 'True'" )

fp <- sqldf("select * from small_ds where malware = 'False' and apidetected = 'True'" )

fn <- sqldf("select * from small_ds where malware = 'True' and apidetected = 'False'" )


precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore

sqldf("select count(*) from small_ds where family = 'None'")

families <- sqldf("select family, count(*) as Total 
                   from small_ds where family != 'None'
                   group by family 
                  order by 2 desc")

sqldf("select family, total*100.0/69.0
       from families 
       order by 2 desc")

sqldf("select malware, apidetected, count(*) 
       from small_ds 
       group by malware, apidetected")
```

### Comparing the similarity scores (complete and small datasets)

```{r similarityComparison}
summary(small_ds$similarity)
summary(full_ds$similarity)

sd(small_ds$similarity)
sd(full_ds$similarity)


sds <- sqldf("select similarity, 'Small Dataset' as dataset from small_ds") 
cds <- sqldf("select similarity, 'Complete Dataset' as dataset from full_ds") 

ds <- rbind(sds, cds)

ds$dataset <- factor(ds$dataset , levels=c("Small Dataset", "Complete Dataset"))


boxplot(similarity~dataset, data = ds, xlab="Datasets", ylab="Similarity Score")
```

### Logistic regression (on similarity)

```{r glm}
s1 <- sqldf("select ds.*, 1 as h1 
             from full_ds ds 
             where (malware = 'True' and apidetected = 'True') or 
                   (malware = 'False' and apidetected = 'False')")

s2 <- sqldf("select ds.*, 0 as h1 
             from full_ds ds
             where (malware = 'True' and apidetected = 'False') or 
                   (malware = 'False' and apidetected = 'True')")

ds <- rbind(s1, s2)


ds$h1 <- as.factor(ds$h1)


nrow(ds)

sqldf("select h1, count(*) from ds group by h1")

model <- glm(h1~similarity, data=ds, family = "binomial")

summary(model)
```

### Clustering assessment (on similarity)

```{r clusterinigSimilarity}
set.seed(123)

km.res <- kmeans(ds$similarity, 5)

print(km.res)

dd <- cbind(ds, cluster = km.res$cluster)

head(dd)

s1 <- sqldf("select cluster, count(*) as total from dd group by cluster")
s2 <- sqldf("select cluster, count(*) as hits from dd where h1 = 1 group by cluster")

dd = merge(s1, s2)

dd["Percent"] = dd$hits * 100 / dd$total

dd 

## 1 0.1119763
## 2 0.8261275
## 3 0.9653697
## 4 0.4371995
## 5 0.6751769

cs = data.frame("cluster" = c(1,2,3,4,5), 
                "averageSimilarity" = c(0.11, 0.82, 0.96, 0.43, 0.67))

cs = merge(dd, cs)

colnames(cs)

xtable(sqldf("select cluster, averageSimilarity, total, hits, percent 
              from cs 
              order by averageSimilarity"))

```
