---
title: "Dataset Merge"
author: "anonymous"
date: '2022-10-14'
output: html_document
description: This script create our final dataset file for analysis - sample_final_ds.csv.csv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=5, fig.height=5, fig.path='./figures/', dev=c('png', 'pdf'))

setwd(".")

library(sqldf)
library(xtable)
```

## Merge Script


The purpose of this R script is to merge several datasets into a single one. 
The following datasets are merged:

   * *appsHash* contains the hash of all apps, including information to indicate 
   if a given asset is an original or a repackaged version of an app. 
   
   * *avclass* contains the results of using the tool av2class to identify 
   the family of the malware in our dataset. 
   
   * *originalMalwareSample* contains the hash of the apps used in the 
   Bao et al. study. 
   
   * *summaryTypeFamily.csv* contains the outputs of the mining android sandbox 
   approach. 
   
We merge the above datasets and export the results to a file named *final-ds.csv*.   

```{r vt}

#Load the Datasets
apps <- read.csv("appsHash.csv", head=T, sep=',')

repackaged <- sqldf("select repackage from apps ")

nrow(repackaged)

avclass <- read.csv("avclass.csv", head=T, sep=',')

nrow(avclass)

firstPart <- sqldf("select a.original as original,a.repackage as sha256,c.family as family from apps a 
                     inner join avclass c on a.repackage = c.sha256")

firstStep <- sqldf("select a.original as original,a.repackage as sha256,c.family as family from apps a 
                     inner join avclass c on a.repackage = c.sha256")

originalFamily <- read.csv("originalSampleFamily.csv", head=T, sep=',')

originalFamily <- sqldf("select * from originalFamily ")

secondStep <- sqldf("select f.original as sha256original,
                     case
	                     when (o.family isNull) THEN 'True'
	                  Else 'False'
                     END as benign,
                     case
	                     when (o.qt isNull) THEN '0'
	                  Else o.qt
                     END as vendorbenign,
                     f.sha256 as sha256,f.family as family,
                     case
	                     when (f.family = 'None') THEN 'False'
	                  Else 'True'
                     END as malware
                     
                     from firstStep f 
                     left join originalFamily o on f.original = upper(o.hash)")

nrow(secondStep)

malwareFamily <- read.csv("repackageSampleFamily.csv", head=T, sep=',')
malwareFamily <- sqldf("select * from malwareFamily")

result <- read.csv("methods_explored/output/diffs/summary.csv")
result <- sqldf("select * from result")


write.csv(result, "av.csv", quote = F, row.names = F)


s1 <- sqldf("select r.app, r.hash, a.family as family, 'True' as Malware
				from repackaged r, avclass a where r.hash = a.sha256")
						 

s2 <- sqldf("select r.app, r.hash, 'None' as family, 'False' as Malware
                   from repackaged r
                   where r.hash not in (select a.sha256 from avclass a)")

nrow(s1)

nrow(s2)

ds <- rbind(s1, s2)



masResults <- read.csv("summarySimiDroid.csv", head=T)

final_ds <- sqldf("select substring(ds.app,11) as app, ds.hash as hash, ds.family as family, ds.Malware as malware from ds")

colnames(final_ds)
head(final_ds)


 write.csv(final_ds, "final-ds.csv",  quote = F, row.names = F)
```




