---
title: "MiningSandbox"
author: "Rodrigo Bonifácio et al."
date: '2023-01-23'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=5, fig.height=5, fig.path='./figures/', dev=c('png', 'pdf'))
setwd(".")
library(sqldf)
```


```{r setup, include=FALSE}
library(xtable)
```


# Loading and cleaning up the datasets

```{r fullDataSet}
#full_ds <- read.csv("sample_final_ds.csv", head=T, sep=',')
full_ds <- read.csv("sample_final_ds_before_VT_check.csv", head=T, sep=',')
small_ds <- read.csv("samples_DL_final_ds.csv", head=T, sep=',')


colnames(full_ds)
nrow(full_ds)

full_ds <- sqldf("select * from full_ds where benign = 'True'")

#full_ds$similarity <- as.numeric(gsub(",", ".", gsub("\\.", "", full_ds$similarity)))
#options(digits=15)
full_ds$similarity = as.numeric(as.character(full_ds$similarity))

#as.numeric("1244713607364931585"),digits=15

write.csv(full_ds, "sample_final_ds_after_VT_check.csv", quote = F, row.names = F)


nrow(full_ds)

# "sha256"      "family"      "malware"     "apidetected" "similarity"
```

# Initial Assessment

## Number of malwares (complete dataset)

```{r countMalwareCDS}
sqldf("select malware, count(*) from full_ds group by malware")
```

## Number of repackaged apps the MAS approach labels as malware (complete dataset)

```{r countLabeledAsMalwareCDS}
sqldf("select apidetected, count(*) from full_ds group by apidetected")

sqldf("select malware, apidetected, count(*) 
       from full_ds 
       group by malware, apidetected")
```

# Section 4.1

## Accuracy Assessment (small dataset)

```{r smallDataSet}
sqldf("select malware, apidetected, count(*) 
       from small_ds 
       group by malware, apidetected")


rp <- sqldf("select count(*) from small_ds where malware = 'True'")

tp <- sqldf("select * from small_ds where malware = 'True' and apidetected = 'True'" )

fp <- sqldf("select * from small_ds where malware = 'False' and apidetected = 'True'" )

fn <- sqldf("select * from small_ds where malware = 'True' and apidetected = 'False'" )


precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore

sqldf("select count(*) from small_ds where family = 'None'")

families <- sqldf("select family, count(*) as Total 
                   from small_ds where family != 'None'
                   group by family 
                  order by 2 desc")

sqldf("select family, total*100.0/69.0
       from families 
       order by 2 desc")

sqldf("select malware, apidetected, count(*) 
       from small_ds 
       group by malware, apidetected")
```

## Accuracy assesment (complete dataset)

```{r accuracyCDS}

tp <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'True'" )

fp <- sqldf("select * from full_ds where malware = 'False' and apidetected = 'True'" )

fn <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'False'" )

precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore

```
# Section 4.2 (Similarity Assessment)

## Computing basic statistics for similarity 

```{r similarityCDS}
summary(small_ds$similarity)
sd(small_ds$similarity)

summary(full_ds$similarity)
sd(full_ds$similarity)

sqldf("select count(*) from full_ds where similarity = 0")

sqldf("select count(*) from full_ds where similarity < 0.25")
sqldf("select count(*)  from full_ds where similarity >= 0.25 and similarity < 0.5")
sqldf("select count(*)  from full_ds where similarity >= 0.5 and similarity < 0.75")
sqldf("select count(*)  from full_ds where similarity >= 0.75")
sqldf("select count(*)  from full_ds where similarity >= 0.90")

```
### Comparing the similarity scores (complete and small datasets)

```{r similarityComparison}
summary(small_ds$similarity)
summary(full_ds$similarity)

sd(small_ds$similarity)
sd(full_ds$similarity)


sds <- sqldf("select similarity, 'Small Dataset' as dataset from small_ds") 
cds <- sqldf("select similarity, 'Complete Dataset' as dataset from full_ds") 

ds <- rbind(sds, cds)

ds$dataset <- factor(ds$dataset , levels=c("Small Dataset", "Complete Dataset"))


boxplot(similarity~dataset, data = ds, xlab="Datasets", ylab="Similarity Score", col = c("gray"), outline=F)
```

### Logistic regression (on similarity)

```{r glm}


#s1 <- sqldf("select ds.*, 'True' as h1 
#             from full_ds ds 
#             where (malware = 'True' and apidetected = 'True') or 
#                   (malware = 'False' and apidetected = 'False')")

s1 <- sqldf("select ds.*, 'True' as h1 
             from full_ds ds 
             where (malware = 'True' and apidetected = 'True')")

s2 <- sqldf("select ds.*, 'False' as h1 
             from full_ds ds
             where (malware = 'True' and apidetected = 'False') or 
                   (malware = 'False' and apidetected = 'True')")

ds <- rbind(s1, s2)


ds$h1 <- as.factor(ds$h1)

# cor.test(ds$h1, ds$similarity)

nrow(ds)

sqldf("select h1, count(*) from ds group by h1")

model <- glm(h1~similarity, data=ds, family = "binomial")

summary(model)
```

### Clustering assessment (on similarity)

```{r clusterinigSimilarity}
set.seed(123)

km.res <- kmeans(ds$similarity, 10)

print(km.res)

dd <- cbind(ds, cluster = km.res$cluster)

head(dd)

s1 <- sqldf("select cluster, count(*) as total from dd group by cluster")
s2 <- sqldf("select cluster, count(*) as hits from dd where h1 = 'True' group by cluster")

dd = merge(s1, s2)

dd["Percent"] = dd$hits * 100 / dd$total

dd 

## 1  0.0206422
## 2  0.4930103
## 3  0.9980512
## 4  0.9467957
## 5  0.9892665
## 6  0.8090455
## 7  0.7194053
## 8  0.9725808
## 9  0.9125622
## 10 0.8801738

cs = data.frame("cluster" = c(1,2,3,4,5, 6, 7, 8, 9, 10), 
                "averageSimilarity" = c(0.02, 0.49, 0.99, 0.94, 0.98,0.80,0.71,0.97, 0.91, 0.88))

cs = merge(dd, cs)

colnames(cs)

xtable(sqldf("select cluster, averageSimilarity, total, hits, percent 
              from cs 
              order by averageSimilarity"))


km.res <- kmeans(ds$similarity, 5)

print(km.res)

dd <- cbind(ds, cluster = km.res$cluster)

head(dd)

s1 <- sqldf("select cluster, count(*) as total from dd group by cluster")
s2 <- sqldf("select cluster, count(*) as hits from dd where h1 = 'True' group by cluster")

dd = merge(s1, s2)

dd["Percent"] = dd$hits * 100 / dd$total

dd 

## 1 0.0409438
## 2 0.9878021
## 3 0.7776560
## 4 0.5158275
## 5 0.8988103

cs = data.frame("cluster" = c(1,2,3,4,5), 
                "averageSimilarity" = c(0.04, 0.98, 0.77, 0.51, 0.89))

cs = merge(dd, cs)

colnames(cs)

xtable(sqldf("select cluster, averageSimilarity, total, hits, percent 
              from cs 
              order by averageSimilarity"))


```
# Section 5
## Accuracy assesment (complete dataset with parameter help)

```{r accuracyCDS}

tp <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'True' or paramdetected = 'True')" )

fp <- sqldf("select * from full_ds where malware = 'False' and (apidetected = 'True' or paramdetected = 'True')" )

fn <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'False' and paramdetected = 'False')" )

precisionWithParam = nrow(tp) / (nrow(tp) + nrow(fp))

recallWithParam = nrow(tp) / (nrow(tp) + nrow(fn))

fscoreWithParam = 2 * (precisionWithParam*recallWithParam) / (precisionWithParam + recallWithParam)

precisionWithParam
recallWithParam
fscoreWithParam
```
## Accuracy assesment (complete dataset with trace help)

```{r accuracyCDS}

tp <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'True' or tracedetected = 'True')" )

fp <- sqldf("select * from full_ds where malware = 'False' and (apidetected = 'True' or tracedetected = 'True')" )

fn <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'False' and tracedetected = 'False')" )

precisionWithTrace = nrow(tp) / (nrow(tp) + nrow(fp))

recallWithTrace = nrow(tp) / (nrow(tp) + nrow(fn))

fscoreWithTrace = 2 * (precisionWithTrace*recallWithTrace) / (precisionWithTrace + recallWithTrace)

precisionWithTrace
recallWithTrace
fscoreWithTrace
```
## Accuracy assesment (complete dataset with parameter and trace help)

```{r accuracyCDS}

tp <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'True' or tracedetected = 'True' or paramdetected = 'True')" )

fp <- sqldf("select * from full_ds where malware = 'False' and (apidetected = 'True' or tracedetected = 'True' or paramdetected = 'True')" )

fn <- sqldf("select * from full_ds where malware = 'True' and (apidetected = 'False' and tracedetected = 'False' and paramdetected = 'False')" )

precisionWithAll = nrow(tp) / (nrow(tp) + nrow(fp))

recallWithAll = nrow(tp) / (nrow(tp) + nrow(fn))

fscoreWithAll = 2 * (precisionWithAll*recallWithAll) / (precisionWithAll + recallWithAll)

precisionWithAll
recallWithAll
fscoreWithAll
```
# Section 6
## Accuracy assesment (complete dataset with just one vendor)

```{r accuracyCDS}

tp <- sqldf("select * from full_ds where (malware = 'True' or qtdvendor = 1) and apidetected = 'True'")

fp <- sqldf("select * from full_ds where (malware = 'False' and qtdvendor = 0) and apidetected = 'True'")

fn <- sqldf("select * from full_ds where (malware = 'True' or qtdvendor = 1) and apidetected = 'False'" )

precision1V = nrow(tp) / (nrow(tp) + nrow(fp))

recall1V = nrow(tp) / (nrow(tp) + nrow(fn))

fscore1V = 2 * (precision1V*recall1V) / (precision1V + recall1V)

precision1V
recall1V
fscore1V
```

### Accuracy assesment (Complete dataset without gappusin)

```{r accuracyCDSWithoutGappusin}

sqldf("select malware, apidetected, count(*) 
       from full_ds 
       where family = 'gappusin'
       group by malware, apidetected")

tp <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'True' and family != 'gappusin'" )

fp <- sqldf("select * from full_ds where malware = 'False' and apidetected = 'True' and family != 'gappusin'" )

fn <- sqldf("select * from full_ds where malware = 'True' and apidetected = 'False' and family != 'gappusin'" )

precision = nrow(tp) / (nrow(tp) + nrow(fp))

recall = nrow(tp) / (nrow(tp) + nrow(fn))

fscore = 2 * (precision*recall) / (precision + recall)

precision
recall
fscore
```


### Similarity Assessment (Gappusin Family)

```{r, similarityGappusin}
# Gappusin family

gappusin <- sqldf("select * from full_ds where family =  'gappusin'")

summary(gappusin$similarity)
sd(gappusin$similarity)
hist(gappusin$similarity, main="", xlab="Similarity Score", ylab="Frequency", col = c("gray"))

```


### Family Assessment (Complete Dataset)

```{r familyAssesmentCDS}
sqldf("select family, count(*) 
       from full_ds 
       where malware = 'True' 
       group by family order by 2 desc")


sqldf("select malware, apidetected, count(*) 
       from full_ds 
       where family = 'gappusin'
       group by malware, apidetected")

sqldf("select count(distinct family) from full_ds")


sqldf("select count(*) from full_ds where family = 'None'")

families <- sqldf("select family, count(*) as Total 
                   from full_ds where family != 'None'
                   group by family 
                  order by 2 desc")

sqldf("select family, total*100.0/2642.0
       from families 
       group by family
       order by 2 desc")
```