---
title: "Dataset Merge"
author: "Francisco Handrick"
date: '2022-10-14'
output: html_document
description: This script create our final dataset file for analysis - sample_final_ds_before_VT_check.csv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=5, fig.height=5, fig.path='./figures/', dev=c('png', 'pdf'))

setwd(".")

library(sqldf)
library(xtable)
```

## Merge Script


The purpose of this R script is to merge several datasets into a single one. 
The following datasets are merged:

   * *appsHash* contains the hash of all apps, including information to indicate 
   if a given asset is an original or a repackaged version of an app. 
   
   * *avclass* contains the results of using the tool av2class to identify 
   the family of the malware in our dataset. 
   
   * *sampleAppHash.csv* contains the hash of the original apps used in our study. 
   
   * *originalSampleFamily* contains the malware family of the original apps used in our study. 
   
   * *repackageSampleFamily.csv* contains the malware family of the repackage apps used in our study. 
   
   * *summary.csv* contains the outputs of the mining android sandbox approach.
   
   * *summarySimiDroid.csv* contains the outputs of Simidroid with similarity of all app pairs.
   
We merge the above datasets and export the results to a file named *sample_f_ds.csv*.   

```{r vt}

#Load the Datasets
apps <- read.csv("appsHash.csv", head=T, sep=',')

repackaged <- sqldf("select repackaged from apps ")

colnames(repackaged)

nrow(repackaged)


avclass <- read.csv("avClassResultRepackaged.csv", head=T, sep=',')
nrow(avclass)

firstPart <- sqldf("select a.original as original,a.repackaged as sha256,c.family as family from apps a 
                     inner join avclass c on a.repackaged = c.sha256_repackaged")
nrow(firstPart)

firstStep <- sqldf("select a.original as original,a.repackaged as sha256,c.family as family from apps a 
                     inner join avclass c on a.repackaged = c.sha256_repackaged")

originalFamily <- read.csv("originalSampleFamily.csv", head=T, sep=',')
originalFamily <- sqldf("select * from originalFamily ")
nrow(originalFamily)

malwareFamily <- read.csv("repackageSampleFamily.csv", head=T, sep=',')
malwareFamily <- sqldf("select * from malwareFamily")
nrow(malwareFamily)

result <- read.csv("../methods_explored/output/diffs/summary.csv")
result <- sqldf("select * from result")
nrow(result)

apphash <- read.csv("sampleAppHash.csv", head=T, sep=',')
apphash <- sqldf("select * from apphash")


secondStep <- sqldf("select f.original as sha256original,
                     o.benign as benign,
	                  
                     f.sha256 as sha256,f.family as family,
                     case
	                     when (f.family = 'None') THEN 'False'
	                  Else 'True'
                     END as malware,
                     case
	                     when (r.methods_in_diff = '0') THEN 'False'
	                  Else 'True' 
	                  END as apidetected
                     
                     from firstStep f 
                     
                     left join originalFamily o on f.original = o.hash
                     inner join apphash h on h.hash = f.sha256
                     inner join result r on r.apk = h.app")



simiResults <- read.csv("summarySimiDroid.csv", head=T)
simiResults <- sqldf("select * from simiResults")

thirdStep <- sqldf("select s.*,r.identical,r.similar,r.new,r.deleted,r.simiscore from 
                   secondStep s 
                   inner join simiResults r on s.sha256 = r.sha256
                   inner join malwareFamily m on s.sha256 = m.sha256repackage")

nrow(thirdStep)
write.csv(thirdStep, "sample_final_ds_before_VT_check.csv", quote = F, row.names = F)

```

```{r vt}





